---
title: "linregvignette"
author: "Chao Fu & Michael Bailey"
data: "r Sys.Date()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linregvignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(regression)
```
# Description
Implement the linear regression algorithm as lm() and specified print out with S3 class.

# Functions

## linreg
1. The function calculates the linear regression algorithm. 
1. The return is an object containing a list data and the class of "linreg".

## print()
1. A method belongs to the class of "linreg".
1. The return contains a linear expression as the arguments in linreg's function and it's coefficients.

## plot()
1. A method belongs to the class of "linreg".
1. The return contains two graphs using ggplot2.
1. The first graph is that x is Fitted values and y is Residuals. The second graph is that x is Fitted values and y is $\sqrt{|Standardized residuals|}.

## resid()
1. A method belongs to the class of "linreg".
1. The return is the vector of residuals e.

## pred()
1. A method belongs to the class of "linreg".
1. The return is the predicted values of y.

## coef()
1. A method belongs to the class of "linreg".
1. The return is the coefficients as a named vector.

## summary()
1. A method belongs to the class of "linreg".
1. The return contains a table with coefficients, their standard error, t-value, p-value and a sentence with the estimate of \sigma and the degree of freedom in the model as the summary().

# Usage

## Install

```{r}
devtools::install_github("chafu696/Lab-4")

```

## Example
```{r}
linlist <- linreg(Petal.Length ~ Species, data = iris)
print(linlist)
plot(linlist)
resid(linlist)
pred(linlist)
coef(linlist)
summary(linlist)
```

